---
title: "proposal"
author: "Ahsan Ghani"
date: "14/02/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Note to Students

This proposal encompasses the following:

1. idea
2. idea
3. idea
4. idea

# Preliminaries

```{r setup, echo=FALSE, cache=FALSE}
## recommended libraries
library(knitr)
library(rmdformats)
## Global options
options(max.print="100")
opts_chunk$set(comment=NA)
opts_knit$set(width=75)
```

## My R Packages

```{r load_packages_here, message = FALSE}
library(janitor)
library(magrittr)
library(naniar)
library(tidyverse)
```

## Data Ingest

notes about the dataset.

The code below actually loads in the data. 

```{r read_in_data_here, message = FALSE}
data_url <- "h"
chr_2019_raw <- read_csv(data_url, skip = 1, guess_max = 4000)
```

# Preprocessing

## ETL


## EDA


### Final Dataframes


## Creating Binary Categorical Variables


# Code Repository

Variable | Description
--------- | ------------------------------------------------
x | x is x
y | y is y
z | z is z

## Proposal Requirement 1 

## Proposal Requirement 2

## Proposal Requirement 3

## Proposal Requirement 4

## Proposal Requirement 5

# Analyses
